---
title: "Human Memory"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---


```{r load, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(viridis)
library(RColorBrewer)
library(colorspace)
library(ggrepel)
library(colorblindr)
library(gghighlight)
library(plotly)
library(ggplot2)
library(scales)
library(lme4)
library(emmeans)
library(dplyr)
library(tidyr)
library(readr)
library(afex)
library(paletteer)
library(readxl)
library(colorblindr)
library(gt)

# Load data 
raw_df <- read.csv("combined_data.csv")

library(showtext)
font_add_google("IBM Plex Sans", "ibm")
showtext_auto()
```

```{r css, echo=FALSE}
htmltools::tags$style("
  @import url('https://fonts.googleapis.com/css2?family=IBM+Plex+Sans:wght@400;600;700&display=swap');

  body, .navbar, .nav-tabs, .tab-content, .sidebar {
    font-family: 'IBM Plex Sans', sans-serif;
  }
  .navbar-inverse {
    background-color: #1F3A6E;
    border-color: #1F3A6E;
  }
  .navbar-inverse .navbar-brand {
    color: #FFFFFF;
    font-size: 22px;
    font-weight: 600;
    font-family: 'IBM Plex Sans', sans-serif;
  }
  .navbar-inverse .navbar-nav > li > a {
    color: #FFFFFF;
    font-size: 17px;
    font-family: 'IBM Plex Sans', sans-serif;
  }
  .navbar-inverse .navbar-nav > .active > a {
    background-color: #2E5499;
    color: #FFFFFF;
    font-weight: 700;
  }
  .navbar-inverse .navbar-nav > li > a:hover {
    background-color: #2E5499;
    color: #FFFFFF;
  }
")
```

# Sidebar {.sidebar}

### About

Authors: Isha Chhabra, America Romero, Ziyuan Chen

We recently collected the Multimodal Memory Dataset in our lab. We collected up to 15 sessions per participant (n=3). In each session, participants learned and recalled image-word pairs. By manipulating how participants learn (encode) and recall image-word pairs, we are interested in how memory performance is affected by various conditions and individual differences in confidence as well as sleep quality. Our intended audience is the general memory researchers. 


# Accuracy vs. Confidence

## Column {data-width="650"}

### Final Version

```{r fig.width=11, fig.height=6.6}
conf_df <- raw_df %>%
  mutate(
    enCon_label = factor(enCon, levels = c(1, 2, 3),
                         labels = c("Single", "Repeats", "Triplets")),
    reCon_label = factor(reCon, levels = c(1, 2),
                         labels = c("Within Session", "Across Sessions")),
    confidence  = factor(
      ifelse(resp %in% c(1, 4), "High Confidence", "Low Confidence"),
      levels = c("High Confidence", "Low Confidence")
    ),
    subjId = factor(subjId)
  )
sess_subj <- conf_df %>%
  group_by(subjId, session, confidence) %>%
  summarise(accuracy = mean(trial_accuracy), .groups = "drop")

sess_mean <- sess_subj %>%
  group_by(session, confidence) %>%
  summarise(
    mean_acc = mean(accuracy),
    se_acc   = sd(accuracy) / sqrt(n()),
    .groups  = "drop"
  )

conf_pal <- c("High Confidence" = "#D55E00", "Low Confidence" = "#E69F00")
conf_lty <- c("High Confidence" = "solid",   "Low Confidence" = "dashed")
subj_pal <- c("3" = "#009E73", "4" = "#0072B2", "5" = "#CC79A7")

pline <- ggplot() +

  # SE ribbon — one per confidence level
  geom_ribbon(
    data  = sess_mean,
    aes(x = session, ymin = mean_acc - se_acc,
        ymax = mean_acc + se_acc,
        fill = confidence, group = confidence),
    alpha = 0.12
  ) +

  # Individual spaghetti lines — coloured by participant,
  # linetype by confidence so both dimensions are visible
  geom_line(
    data  = sess_subj,
    aes(x        = session,
        y        = accuracy,
        colour   = factor(subjId),
        linetype = confidence,
        group    = interaction(subjId, confidence)),
    linewidth = 0.9, alpha = 0.45
  ) +

  # Bold group mean lines
  geom_line(
    data  = sess_mean,
    aes(x        = session,
        y        = mean_acc,
        colour   = confidence,
        linetype = confidence,
        group    = confidence),
    linewidth = 2.8, alpha = 0.95
  ) +

  # Mean points
  geom_point(
    data   = sess_mean,
    aes(x = session, y = mean_acc, fill = confidence, group = confidence),
    shape  = 21, size = 3.5, colour = "white", stroke = 1.8
  ) +

  scale_colour_manual(
    values = c(
      "3" = "#009E73", "4" = "#0072B2", "5" = "#CC79A7",
      "High Confidence" = "#D55E00",
      "Low Confidence"  = "#E69F00"
    ),
    breaks = c("High Confidence", "Low Confidence", "3", "4", "5"),
    labels = c(
      "High Confidence" = "High Confidence",
      "Low Confidence"  = "Low Confidence",
      "3" = "Participant 1", "4" = "Participant 2", "5" = "Participant 3"
    ),
    name = NULL
  ) +
  scale_fill_manual(
    values = conf_pal,
    guide  = "none"
  ) +
  scale_linetype_manual(
    values = conf_lty,
    guide  = "none"   # linetype already shown via colour legend
  ) +
  scale_x_continuous(breaks = 1:15, expand = expansion(add = 0.3)) +
  scale_y_continuous(
    limits = c(0.3, 1.04),   # was c(0.45, 1.04)
    breaks = c(0.5, 0.6, 0.7, 0.8, 0.9, 1.0),
    labels = percent_format()
  ) +

  labs(
    title = "Memory Accuracy by Confidence Level Across Sessions",
    x     = "Session Number",
    y     = "Accuracy"
  ) +

theme_minimal(base_size = 14, base_family = "ibm") +
theme(
    plot.background    = element_rect(fill = "white", colour = NA),
    panel.background   = element_rect(fill = "white", colour = NA),
    panel.grid.major.x = element_blank(),
    panel.grid.minor   = element_blank(),
    panel.grid.major.y = element_line(color = "gray85", linewidth = 0.5),
    axis.line          = element_blank(),
    axis.ticks         = element_blank(),
    plot.title         = element_text(hjust = 0, size = 22, face = "bold", margin = margin(b = 10)),
    legend.position    = "bottom",
    legend.text        = element_text(size = 12),
    legend.key.width   = unit(1.8, "cm"),
    axis.title.x       = element_text(size = 16, colour = "gray30", face = "plain"),
    axis.title.y       = element_text(size = 17, colour = "gray30", vjust = 0.5),
    axis.text          = element_text(size = 13, colour = "gray30"),
    plot.margin        = margin(t = 10, r = 15, b = 30, l = 10)
  )
pline


# Make it interactive
# pline_interactive <- ggplotly(pline, tooltip = c("x", "y")) %>%
#   layout(
#     title  = list(text = "<b>Memory Accuracy by Confidence Level Across Sessions</b>",
#                   font = list(size = 22, color = "black"), x = 0),
#     margin = list(t = 80, r = 20, b = 80, l = 20),
#     xaxis  = list(title = list(text = "Session Number", font = list(size = 16)),
#                   tickfont = list(size = 14),
#                   showgrid = FALSE, zeroline = FALSE),
#     yaxis  = list(title = list(text = "Accuracy", font = list(size = 16)),
#                   tickfont = list(size = 14),
#                   tickformat = ".0%",
#                   gridcolor = "rgba(0,0,0,0.1)"),
#     legend = list(orientation = "h", x = 0, y = -0.15,
#                   font = list(size = 14)),
#     plot_bgcolor  = "white",
#     paper_bgcolor = "white",
#     font = list(color = "gray30", size = 14)
#   )
# 
# # Fix marker sizes to match PNG
# for (i in seq_along(pline_interactive$x$data)) {
#   trace <- pline_interactive$x$data[[i]]
#   if (!is.null(trace$mode) && grepl("markers", trace$mode)) {
#     pline_interactive$x$data[[i]]$marker$size <- 10
#     pline_interactive$x$data[[i]]$marker$line <- list(color = "white", width = 2)
#   }
# }
# 
# pline_interactive
```

## Column {.tabset data-width="350"}

### About

**Research Question:** Is there a difference in memory accuracy based on how confident participants are about their responses?

&nbsp;

**Hypothesis:** Memory performance will be decreased for low confidence responses.

&nbsp;

**Overall:** Confidence and accuracy are strongly positively related. High-confidence trials outperformed low-confidence trials by ~23% points across 3,234 total trials. The larger SD in low-confidence trials indicates genuine uncertainty — participants are sometimes right, but far less consistently. The two confidence levels tend to co-vary across sessions, suggesting shared session-level factors like fatigue or task difficulty.

&nbsp;

```{r}
desc_sess <- sess_subj %>%
  group_by(confidence) %>%
  summarise(
    Sessions = n_distinct(session),
    Mean     = mean(accuracy),
    SD       = sd(accuracy),
    Min      = min(accuracy),
    Max      = max(accuracy),
    .groups  = "drop"
  )

desc_sess %>%
  gt() %>%
  tab_header(
    title    = "Memory Accuracy by Confidence Level",
    subtitle = "Collapsed across sessions and subjects"
  ) %>%
  cols_label(
    confidence = "Confidence",
    Sessions   = "N (sessions)",
    Mean       = "Mean Accuracy",
    SD         = "SD",
    Min        = "Min",
    Max        = "Max"
  ) %>%
  fmt_percent(columns = c(Mean, SD, Min, Max), decimals = 1) %>%
  tab_footnote(
    footnote  = "Min/Max reflect subject-level session means (n = 3 subjects).",
    locations = cells_column_labels(columns = c(Min, Max))
  ) %>%
  tab_style(
    style     = cell_text(weight = "bold"),
    locations = cells_column_labels()
  ) %>%
  opt_row_striping() %>%
  opt_table_font(font = google_font("IBM Plex Sans"))
```


### Old Version 1

```{r}
# ── Shared palette & theme ───────────────────────────────────
PAPER <- "#FAFAF8"
INK   <- "#1C1C1E"
MID   <- "#888888"
LIGHT <- "#E8E8E8"

# Encoding conditions (teal / salmon-orange / slate-blue – matching figure)
enc_pal <- c(
  "Single"   = "#6BBFA0",
  "Repeats"  = "#F0956A",
  "Triplets" = "#8FA8C8"
)

# Confidence  (blue / orange)
conf_pal <- c(
  "High Confidence" = "#2D7DD2",
  "Low Confidence"  = "#E07B4F"
)

# Subject lines  (3 distinct, muted)
subj_pal <- c("3" = "#A07CC5", "4" = "#5B9E8C", "5" = "#C47A5C")

theme_mem <- function(base_size = 12) {
  theme_minimal(base_size = base_size) %+replace%
    theme(
      plot.background    = element_rect(fill = PAPER, colour = NA),
      panel.background   = element_rect(fill = PAPER, colour = NA),
      panel.grid.major.x = element_blank(),
      panel.grid.minor   = element_blank(),
      panel.grid.major.y = element_line(colour = LIGHT, linewidth = 0.5),
      axis.ticks         = element_blank(),
      axis.text          = element_text(colour = MID,  size = 10),
      axis.title         = element_text(colour = MID,  size = 11),
      plot.title         = element_text(face = "bold", colour = INK,
                                        size = 14, hjust = 0),
      plot.subtitle      = element_text(colour = MID, size = 10,
                                        hjust = 0, face = "italic",
                                        margin = margin(b = 10)),
      plot.caption       = element_text(colour = "#BBBBBB", size = 8,
                                        hjust = 0, margin = margin(t = 8)),
      legend.background  = element_rect(fill = PAPER, colour = NA),
      legend.key         = element_rect(fill = PAPER, colour = NA)
    )
}
# Recode confidence levels
confidence_data <- conf_df %>%
  mutate(
    confidence_level = case_when(
      resp %in% c(1, 4) ~ "High",
      resp %in% c(2, 3) ~ "Low"
    ),
    subject_label = factor(subjId, levels = c(3, 4, 5), labels = c("1", "2", "3"))
  )

# Compute mean accuracy per session, confidence level, and participant
confidence_summary <- confidence_data %>%
  group_by(session, confidence_level, subjId, subject_label) %>%
  summarise(mean_accuracy = mean(trial_accuracy, na.rm = TRUE), .groups = "drop")

# Create the plot
ggplot(confidence_summary, aes(x = session, y = mean_accuracy, 
                                      color = subject_label, 
                                      linetype = confidence_level,
                                      group = interaction(subjId, confidence_level))) +
  geom_line(size = 1.2) +
  geom_point(size = 3.5) +
  labs(
    title = "Accuracy Trends Across Sessions by Confidence Level",
    x = "Session Number",
    y = "Mean Accuracy",
    color = "Subject",
    linetype = "Confidence Level"
  ) +
  scale_x_continuous(breaks = 1:15) +
  scale_y_continuous(
    limits = c(0.45, 1.05), 
    breaks = seq(0.5, 1.0, by = 0.1),
    labels = percent_format(accuracy = 1)
  ) +
  scale_color_brewer(palette = "Set1") +
  scale_linetype_manual(values = c("High" = "solid", "Low" = "dashed")) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    legend.box = "horizontal",
    legend.margin = margin(t = 10),
    panel.grid.minor = element_blank(),
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    axis.title = element_text(size = 12, face = "bold"),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11, face = "bold"),
    legend.text = element_text(size = 10),
    plot.margin = margin(10, 10, 10, 10)
  )

```

### Old Version 2
```{r}
ggplot() +

  # SE ribbon around group mean
  geom_ribbon(
    data  = sess_mean,
    aes(x = session, ymin = mean_acc - se_acc,
        ymax = mean_acc + se_acc, fill = confidence),
    alpha = 0.15
  ) +

  # Individual participant spaghetti lines
  geom_line(
    data      = sess_subj,
    aes(x = session, y = accuracy, colour = subjId, group = subjId),
    linewidth = 0.9, alpha = 0.50
  ) +

  # Bold group mean line
  geom_line(
    data      = sess_mean,
    aes(x = session, y = mean_acc, colour = confidence),
    linewidth = 2.0, alpha = 0.9
  ) +

  # Mean points
  geom_point(
    data   = sess_mean,
    aes(x = session, y = mean_acc, fill = confidence),
    shape  = 21, size = 3.5, colour = "white", stroke = 1.8
  ) +

  facet_wrap(~ confidence, ncol = 2) +

  scale_colour_manual(
    values = c(
      "3" = "#A07CC5", "4" = "#5B9E8C", "5" = "#C47A5C",
      "High Confidence" = "#2D7DD2",
      "Low Confidence"  = "#E07B4F"
    ),
    breaks = c("3", "4", "5"),
    name   = "Participant",
    labels = c("3" = "1", "4" = "2", "5" = "3")
  ) +
  scale_fill_manual(
    values = c(
      "High Confidence" = "#2D7DD2",
      "Low Confidence"  = "#E07B4F"
    ),
    guide = "none"
  ) +
  scale_x_continuous(breaks = 1:15, expand = expansion(add = 0.3)) +
  scale_y_continuous(
    limits = c(0.48, 1.05),
    breaks = c(0.5, 0.6, 0.7, 0.8, 0.9, 1.0),
    labels = percent_format()
  ) +

  labs(
    title    = "Memory Accuracy by Confidence Level Across Sessions",
    subtitle = "Bold line = group mean +/- 1 SE ribbon  |  Thin lines = individual participants",
    x        = "Session Number",
    y        = "Accuracy",
    caption  = paste(
      "High confidence = sure responses (resp 1 or 4).",
      "Low confidence = maybe responses (resp 2 or 3)."
    )
  ) +

  theme_mem() +
  theme(
    strip.text       = element_text(face = "bold", size = 11, colour = INK),
    strip.background = element_rect(fill = PAPER, colour = NA),
    panel.spacing    = unit(1.5, "lines"),
    legend.position  = "bottom",
    legend.title     = element_text(face = "bold", size = 9),
    legend.text      = element_text(size = 9)
  )
```



# Accuracy vs. Memory Conditions

## Column {data-width="650"}

### Final Version

```{r fig.width=10, fig.height=6}
# ============================================================
#  Memory Accuracy – Visualization Script
# ── Load & recode ────────────────────────────────────────────
# conf_df <- raw_df %>%
#   mutate(
#     enCon_label = factor(enCon, levels = c(1, 2, 3),
#                          labels = c("Single", "Repeats", "Triplets")),
#     reCon_label = factor(reCon, levels = c(1, 2),
#                          labels = c("Within Session", "Across Sessions")),
#     confidence  = factor(
#       ifelse(resp %in% c(1, 4), "High Confidence", "Low Confidence"),
#       levels = c("High Confidence", "Low Confidence")
#     ),
#     subjId = factor(subjId)
#   )

# ── Shared palette & theme ───────────────────────────────────
PAPER <- "#FAFAF8"
INK   <- "#1C1C1E"
MID   <- "#888888"
LIGHT <- "#E8E8E8"

enc_pal <- c(
  "Single"   = "#999999",
  "Repeats"  = "#D55E00",
  "Triplets" = "#56B4E9"
)

subj_shapes <- c("3" = 15, "4" = 17, "5" = 16)  # square, triangle, circle

theme_mem <- function(base_size = 12) {
  theme_minimal(base_size = base_size) %+replace%
    theme(
      plot.background    = element_rect(fill = PAPER, colour = NA),
      panel.background   = element_rect(fill = PAPER, colour = NA),
      panel.grid.major.x = element_blank(),
      panel.grid.minor   = element_blank(),
      panel.grid.major.y = element_line(colour = LIGHT, linewidth = 0.5),
      axis.ticks         = element_blank(),
      axis.text          = element_text(colour = MID, size = 10),
      axis.title         = element_text(colour = MID, size = 11),
      plot.title         = element_text(face = "bold", colour = INK,
                                        size = 14, hjust = 0),
      plot.subtitle      = element_text(colour = MID, size = 10,
                                        hjust = 0, face = "italic",
                                        margin = margin(b = 10)),
      plot.caption       = element_text(colour = "#BBBBBB", size = 8,
                                        hjust = 0, margin = margin(t = 8)),
      legend.background  = element_rect(fill = PAPER, colour = NA),
      legend.key         = element_rect(fill = PAPER, colour = NA)
    )
}


# ============================================================
# Plot

mod <- lmer(
  trial_accuracy ~ enCon_label * reCon_label + (1 | subjId),
  data = conf_df, REML = TRUE
)
# print(summary(mod))

# Step 2: Extract EMMs with 95% CIs
emm_options(pbkrtest.limit = 3500, lmerTest.limit = 3500)
emm_raw <- emmeans(mod, ~ enCon_label * reCon_label)

emm <- confint(emm_raw) %>%
  as.data.frame() %>%
  rename(
    enc      = enCon_label,
    rec      = reCon_label,
    estimate = emmean,
    lower    = lower.CL,
    upper    = upper.CL
  ) %>%
  mutate(
    enc = factor(enc, levels = c("Single", "Repeats", "Triplets")),
    rec = factor(rec, levels = c("Within Session", "Across Sessions")),
    x_group = factor(
      interaction(rec, enc, sep = "__"),
      levels = c(
        "Within Session__Single",   "Within Session__Repeats",   "Within Session__Triplets",
        "Across Sessions__Single",  "Across Sessions__Repeats",  "Across Sessions__Triplets"
      )
    )
  )

#message("-- Estimated Marginal Means --")
#print(emm %>% select(enc, rec, estimate, lower, upper))

# Step 3: Subject-level means for raw data overlay
# FIX: Explicit factor levels set after rename so they always match emm,
# regardless of what order they appear in the raw data.
# FIX: height = 0 in jitter (see plot layer) so y-values are not distorted.
conf_subj_acc <- conf_df %>%
  group_by(subjId, enCon_label, reCon_label) %>%
  summarise(accuracy = mean(trial_accuracy), .groups = "drop") %>%
  rename(enc = enCon_label, rec = reCon_label) %>%
  mutate(
    enc     = factor(enc, levels = c("Single", "Repeats", "Triplets")),
    rec     = factor(rec, levels = c("Within Session", "Across Sessions")),
    x_group = factor(
      interaction(rec, enc, sep = "__"),
      levels = levels(emm$x_group)   # reuse levels from emm — single source of truth
    )
  )

# Step 4: Plot
x_labels <- c("Single", "Repeats", "Triplets", "Single", "Repeats", "Triplets")


ggplot() +

  # Vertical divider between recall groups
  annotate("segment",
         x = 3.5, xend = 3.5, y = 0.48, yend = 1.02,  # was 1.05
         colour = "#DEDEDE", linewidth = 1.2) +

  # Group header labels
  annotate("text", x = 2, y = 0.485, label = "Within Session",
           hjust = 0.5, vjust = 1, size = 5, fontface = "plain", colour = INK) +
  annotate("text", x = 5, y = 0.485, label = "Across Sessions",
           hjust = 0.5, vjust = 1, size = 5, fontface = "plain", colour = INK) +

  # Layer 1: 95% CI error bars with caps on both ends.
  # Upper CI capped at 1.0 so the top cap is always visible —
  # without this, near-ceiling Within Session conditions produce
  # model CIs above 100% that get clipped by the axis, making
  # it look like only the bottom cap is shown.
  geom_errorbar(
    data  = emm %>% mutate(upper = pmin(upper, 1.0)),
    aes(x = x_group, ymin = lower, ymax = upper, colour = enc),
    width = 0.25, linewidth = 1.1
  ) +

  geom_point(
    data     = conf_subj_acc %>% filter(subjId == "3"),
    aes(x = x_group, y = accuracy, colour = enc, shape = subjId),
    position = position_nudge(x = -0.22),
    size = 4, alpha = 0.75, stroke = 0.8
  ) +
  geom_point(
    data     = conf_subj_acc %>% filter(subjId == "4"),
    aes(x = x_group, y = accuracy, colour = enc, shape = subjId),
    position = position_nudge(x = 0.10),
    size = 4, alpha = 0.75, stroke = 0.8
  ) +
  geom_point(
    data     = conf_subj_acc %>% filter(subjId == "5"),
    aes(x = x_group, y = accuracy, colour = enc, shape = subjId),
    position = position_nudge(x = 0.22),
    size = 4, alpha = 0.75, stroke = 0.8
  ) +

  # Layer 3: Model-estimated mean (drawn last — always on top)
  geom_point(
    data   = emm,
    aes(x = x_group, y = estimate, fill = enc),
    shape  = 21, size = 8, stroke = 2.8,
    colour = "white"
  ) +

  scale_colour_manual(values = enc_pal, name = "Encoding Condition") +
  scale_fill_manual(values   = enc_pal, guide = "none") +
  scale_shape_manual(
    values = subj_shapes,
    name   = "Participant",
    labels = c("3" = "1", "4" = "2", "5" = "3")
  ) +
  scale_x_discrete(labels = NULL) +
  scale_y_continuous(
    limits = c(0.47, 1.02),
    breaks = c(0.5, 0.6, 0.7, 0.8, 0.9, 1.0),
    labels = percent_format()
  ) +

  labs(
    title    = "Memory Accuracy Across Conditions",
    x        = "Recall Condition",
    y        = "Accuracy",
    caption  = NULL
  ) +

  guides(
    colour = guide_legend(order = 2,
                          override.aes = list(shape = 16, size = 4, alpha = 1)),
    shape  = guide_legend(order = 1,
                          override.aes = list(colour = "grey40", size = 4, alpha = 1))
  ) +
theme_minimal(base_size = 14, base_family = "ibm") +
theme(
    plot.background    = element_rect(fill = "white", colour = NA),
    panel.background   = element_rect(fill = "white", colour = NA),
    panel.grid.major.x = element_blank(),
    panel.grid.minor   = element_blank(),
    panel.grid.major.y = element_line(color = "gray85", linewidth = 0.5),
    axis.line          = element_blank(),
    axis.ticks         = element_blank(),
    plot.title         = element_text(hjust = 0, size = 22, face = "bold", margin = margin(b = 10)),
    legend.position    = "bottom",
    legend.title       = element_text(face = "bold", size = 13, colour = "gray30"),
    legend.text        = element_text(size = 12),
    legend.spacing.x   = unit(0.5, "cm"),
    axis.title.x       = element_text(size = 16, colour = "gray30", face = "plain"),
    axis.title.y       = element_text(size = 17, colour = "gray30"),
    axis.text          = element_text(size = 13, colour = "gray30"),
    plot.margin        = margin(t = 10, r = 15, b = 30, l = 10),
    plot.clip          = "off"
  )
```

## Column {.tabset data-width="350"}

### About

**Research Question:** Is there a difference in memory accuracy based on how confident participants are about their responses?

&nbsp;

**Hypothesis:** Memory performance will be decreased for low confidence responses.

&nbsp;

**Overall:** Confidence and accuracy are strongly positively related. High-confidence trials outperformed low-confidence trials by ~23 percentage points across 3,234 total trials. The larger SD in low-confidence trials indicates genuine uncertainty — participants are sometimes right, but far less consistently. The two confidence levels tend to co-vary across sessions, suggesting shared session-level factors like fatigue or task difficulty.

&nbsp;

```{r}
# Trial counts at trial level
conf_trial_counts <- conf_df %>%
  group_by(enCon_label, reCon_label) %>%
  summarise(Trials = n(), .groups = "drop")

# Subject-level means
conf_subj_means <- conf_df %>%
  group_by(subjId, enCon_label, reCon_label) %>%
  summarise(subj_acc = mean(trial_accuracy), .groups = "drop")

# Summarise across subjects, join trial counts
desc_conf <- conf_subj_means %>%
  group_by(enCon_label, reCon_label) %>%
  summarise(
    Mean = mean(subj_acc),
    SD   = sd(subj_acc),
    Min  = min(subj_acc),
    Max  = max(subj_acc),
    .groups = "drop"
  ) %>%
  left_join(conf_trial_counts, by = c("enCon_label", "reCon_label")) %>%
  select(reCon_label, enCon_label, Trials, Mean, SD, Min, Max)

desc_conf %>%
  gt(groupname_col = "reCon_label") %>%
  tab_header(
    title    = "Memory Accuracy by Encoding & Recall Condition",
    subtitle = "Descriptive statistics across all trials and subjects"
  ) %>%
  cols_label(
    enCon_label = "Encoding",
    Trials      = "N (trials)",
    Mean        = "Mean Accuracy",
    SD          = "SD",
    Min         = "Min",
    Max         = "Max"
  ) %>%
  fmt_percent(columns = c(Mean, SD, Min, Max), decimals = 1) %>%
  tab_footnote(
    footnote  = "Min/Max reflect subject-level means (n = 3 subjects per condition).",
    locations = cells_column_labels(columns = c(Min, Max))
  ) %>%
  tab_style(
    style     = cell_text(weight = "bold"),
    locations = cells_column_labels()
  ) %>%
  tab_style(
    style     = cell_text(weight = "bold", color = "gray30"),
    locations = cells_row_groups()
  ) %>%
  opt_row_striping() %>%
  opt_table_font(font = google_font("IBM Plex Sans"))
```

### Old Version 1
```{r}
interaction_individual <- conf_df %>%
  mutate(Session_Type = factor(reCon, levels = c(1, 2),
                               labels = c("Within Session", "Across Sessions"))) %>%
  group_by(subjId, Session_Type, enCon_label) %>%
  summarise(mean_accuracy = mean(trial_accuracy, na.rm = TRUE), .groups = "drop") %>%
  mutate(subject_label = factor(subjId, levels = c(3, 4, 5), labels = c("1", "2", "3")))

# Calculate within-subject error bars for each Session_Type separately
calculate_within_subject_ci <- function(data) {
  # Calculate subject means across encoding conditions
  subject_means <- data %>%
    group_by(subjId) %>%
    summarise(subj_mean = mean(mean_accuracy), .groups = "drop")
  
  # Calculate grand mean
  grand_mean_overall <- mean(data$mean_accuracy)
  
  # Normalize data
  normalized <- data %>%
    left_join(subject_means, by = "subjId") %>%
    mutate(normalized_accuracy = mean_accuracy - subj_mean + grand_mean_overall)
  
  # Calculate within-subject SE and CI
  within_ci <- normalized %>%
    group_by(enCon_label) %>%
    summarise(
      grand_mean = mean(mean_accuracy),
      se_within = sd(normalized_accuracy) / sqrt(n()),
      n = n(),
      .groups = "drop"
    ) %>%
    mutate(
      correction = sqrt(n / (n - 1)),
      se_corrected = se_within * correction,
      ci_lower = grand_mean - qt(0.975, df = n - 1) * se_corrected,
      ci_upper = grand_mean + qt(0.975, df = n - 1) * se_corrected
    )
  
  return(within_ci)
}

# Calculate within-subject CIs for each session type
within_session_ci <- interaction_individual %>%
  filter(Session_Type == "Within Session") %>%
  calculate_within_subject_ci() %>%
  mutate(Session_Type = "Within Session")

across_session_ci <- interaction_individual %>%
  filter(Session_Type == "Across Sessions") %>%
  calculate_within_subject_ci() %>%
  mutate(Session_Type = "Across Sessions")

interaction_within <- bind_rows(within_session_ci, across_session_ci) %>%
  mutate(Session_Type = factor(Session_Type, levels = c("Within Session", "Across Sessions")))

# Perform paired t-tests for each encoding condition comparing Within vs Across
#cat("\n=== PAIRED T-TESTS: Within Session vs Across Sessions ===\n")
#cat("Testing for each encoding condition separately:\n\n")

# Test for Single
single_data <- interaction_individual %>%
  filter(enCon_label == "Single") %>%
  select(subjId, Session_Type, mean_accuracy) %>%
  pivot_wider(names_from = Session_Type, values_from = mean_accuracy)

t_single <- t.test(single_data$`Within Session`, single_data$`Across Sessions`, paired = TRUE)
#cat("Single: t =", round(t_single$statistic, 3), ", p =", round(t_single$p.value, 4), "\n")

# Test for Repeats
repeats_data <- interaction_individual %>%
  filter(enCon_label == "Repeats") %>%
  select(subjId, Session_Type, mean_accuracy) %>%
  pivot_wider(names_from = Session_Type, values_from = mean_accuracy)

t_repeats <- t.test(repeats_data$`Within Session`, repeats_data$`Across Sessions`, paired = TRUE)
# cat("Repeats: t =", round(t_repeats$statistic, 3), ", p =", round(t_repeats$p.value, 4), "\n")

# Test for Triplets
triplets_data <- interaction_individual %>%
  filter(enCon_label == "Triplets") %>%
  select(subjId, Session_Type, mean_accuracy) %>%
  pivot_wider(names_from = Session_Type, values_from = mean_accuracy)

t_triplets <- t.test(triplets_data$`Within Session`, triplets_data$`Across Sessions`, paired = TRUE)
# cat("Triplets: t =", round(t_triplets$statistic, 3), ", p =", round(t_triplets$p.value, 4), "\n")

# Apply Bonferroni correction
p_vals <- c(t_single$p.value, t_repeats$p.value, t_triplets$p.value)
p_vals_corrected <- p.adjust(p_vals, method = "bonferroni")

# cat("\nBonferroni-corrected p-values:\n")
# cat("Single: p =", round(p_vals_corrected[1], 4), "\n")
# cat("Repeats: p =", round(p_vals_corrected[2], 4), "\n")
# cat("Triplets: p =", round(p_vals_corrected[3], 4), "\n")

# Prepare significance brackets
sig_tests <- list(
  list(condition = "Single", p_val = p_vals_corrected[1], y_offset = 0),
  list(condition = "Repeats", p_val = p_vals_corrected[2], y_offset = 1),
  list(condition = "Triplets", p_val = p_vals_corrected[3], y_offset = 2)
)

# Create the plot
palette_colors <- RColorBrewer::brewer.pal(3, "Set2")
custom_colors <- c("Single" = palette_colors[1], 
                   "Repeats" = palette_colors[2], 
                   "Triplets" = palette_colors[3])

p_interaction <- ggplot() +
  # Grand mean error bars
  geom_errorbar(data = interaction_within,
                aes(x = Session_Type, ymin = ci_lower, ymax = ci_upper,
                    group = enCon_label, color = enCon_label),
                width = 0.3, size = 0.8,
                position = position_dodge(width = 0.4)) +
  geom_point(data = interaction_within,
             aes(x = Session_Type, y = grand_mean, color = enCon_label),
             size = 6, shape = 18,
             position = position_dodge(width = 0.4)) +
  # Individual subject lines
  geom_line(data = interaction_individual,
            aes(x = Session_Type, y = mean_accuracy,
                group = interaction(subjId, enCon_label), color = enCon_label),
            size = 1, alpha = 0.6,
            position = position_dodge(width = 0.4)) +
  geom_point(data = interaction_individual,
             aes(x = Session_Type, y = mean_accuracy,
                 color = enCon_label, shape = subject_label),
             size = 5, alpha = 1, stroke = 1.2,
             position = position_dodge(width = 0.4)) +
  scale_color_manual(values = custom_colors, name = "Encoding\nCondition") +
  scale_shape_manual(values = c(16, 17, 15), name = "Subject") +
  scale_y_continuous(limits = c(0.5, NA),
                     labels = percent_format(accuracy = 1),
                     breaks = seq(0.5, 1.0, 0.1),
                     expand = expansion(mult = c(0, 0.15))) +
  labs(
    title = "Interaction: Encoding × Recall Condition",
    x = "Recall Condition",
    y = "Mean Accuracy"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "right",
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5, margin = margin(b = 20)),
    axis.title = element_text(size = 13, face = "bold"),
    axis.text = element_text(size = 11),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 11),
    plot.margin = margin(t = 10, r = 15, b = 30, l = 10),
    plot.clip = "off"
  )

# Add significance brackets for each encoding condition
for (test in sig_tests) {
  if (test$p_val < 0.05) {
    stars <- ifelse(test$p_val < 0.001, "***",
                    ifelse(test$p_val < 0.01, "**", "*"))
    sig_label <- sprintf("%s, p = %.4f", stars, test$p_val)
    
    # Get the max y value for this encoding condition
    condition_data <- interaction_within %>% filter(enCon_label == test$condition)
    y_max <- max(condition_data$ci_upper)
    bracket_y <- y_max + 0.02 + (test$y_offset * 0.04)
    
    # Determine x positions with dodge offset
    dodge_offset <- c("Single" = -0.27, "Repeats" = 0, "Triplets" = 0.27)
    x1 <- 1 + dodge_offset[test$condition]
    x2 <- 2 + dodge_offset[test$condition]
    
    p_interaction <- p_interaction +
      annotate("segment", x = x1, xend = x2, y = bracket_y, yend = bracket_y,
               color = custom_colors[test$condition], size = 0.8) +
      annotate("segment", x = x1, xend = x1, y = bracket_y - 0.008, yend = bracket_y,
               color = custom_colors[test$condition], size = 0.8) +
      annotate("segment", x = x2, xend = x2, y = bracket_y - 0.008, yend = bracket_y,
               color = custom_colors[test$condition], size = 0.8) +
      annotate("text", x = (x1 + x2) / 2, y = bracket_y + 0.012, label = sig_label,
               size = 3.5, hjust = 0.5, color = custom_colors[test$condition])
  }
}
p_interaction
```


### Old Version 2
```{r fig.width=7.5, fig.height=5.5}
# ============================================================
# PLOT 1 – Boxplot: Accuracy × Encoding × Retrieval Condition
#
# APPROACH: Use interaction(reCon, enCon) as the x-axis so that
# each of the 6 combinations gets its own dedicated x-position —
# this guarantees no overlap. We then manually relabel the x-axis
# with group labels and add a divider line between the two recall
# conditions.
#
# Data: subject-level means (n = 3 per box).
# Whiskers = min/max (coef = Inf) since n = 3.
# ============================================================

# Step 1: subject-level mean accuracy per cell
subj_acc <- conf_df %>%
  group_by(subjId, enCon_label, reCon_label) %>%
  summarise(accuracy = mean(trial_accuracy), .groups = "drop") %>%
  mutate(
    enCon_label = factor(enCon_label, levels = c("Single", "Repeats", "Triplets")),
    reCon_label = factor(reCon_label, levels = c("Within Session", "Across Sessions")),
    subjId      = factor(subjId),
    x_group     = interaction(reCon_label, enCon_label, sep = "\n")
  ) %>%
  mutate(x_group = factor(x_group, levels = c(
    "Within Session\nSingle",   "Within Session\nRepeats",   "Within Session\nTriplets",
    "Across Sessions\nSingle",  "Across Sessions\nRepeats",  "Across Sessions\nTriplets"
  )))

subj_shapes <- c("3" = 15, "4" = 17, "5" = 16)   # square, triangle, circle

# X-axis tick labels: show only encoding name
x_labels <- c("Single", "Repeats", "Triplets", "Single", "Repeats", "Triplets")

ggplot(subj_acc,
             aes(x      = x_group,
                 y      = accuracy,
                 fill   = enCon_label,
                 colour = enCon_label)) +

  # ── Vertical divider between Within and Across groups ─────
  annotate("segment",
           x = 3.5, xend = 3.5,
           y = 0.50, yend = 1.04,
           colour = "#DEDEDE", linewidth = 1.2) +

  # ── Group labels above x-axis ─────────────────────────────
  annotate("text", x = 2, y = 0.495,
           label = "Within Session",
           hjust = 0.5, vjust = 1, size = 4, fontface = "bold",
           colour = INK) +
  annotate("text", x = 5, y = 0.495,
           label = "Across Sessions",
           hjust = 0.5, vjust = 1, size = 4, fontface = "bold",
           colour = INK) +

  # ── Boxes ─────────────────────────────────────────────────
  geom_boxplot(
    colour        = "#2a2a2a",
    width         = 0.6,
    outlier.shape = NA,
    linewidth     = 0.7,
    alpha         = 0.42,
    coef          = Inf
  ) +

  # ── Individual subject points ─────────────────────────────
  geom_point(
    aes(shape = subjId),
    size        = 5,
    stroke      = 0.7,
    show.legend = TRUE
  ) +

  # ── Scales ───────────────────────────────────────────────
  scale_fill_manual(values = enc_pal, name = "Encoding Condition") +
  scale_colour_manual(values = enc_pal, guide = "none") +
  scale_shape_manual(
    values = subj_shapes,
    name   = "Subject",
    labels = c("3" = "1", "4" = "2", "5" = "3")
  ) +
  scale_x_discrete(labels = x_labels) +
  scale_y_continuous(
    limits = c(0.49, 1.04),
    breaks = c(0.5, 0.6, 0.7, 0.8, 0.9, 1.0),
    labels = scales::percent_format()
  ) +

  labs(
    title   = "Accuracy Distribution Across Conditions",
    x       = "Recall Condition",
    y       = "Mean Accuracy",
    caption = "Box = IQR of participant means  |  Line = median  |  Whiskers = min/max  |  Shapes = individual participants"
  ) +

  guides(
    fill  = guide_legend(order = 2,
                         override.aes = list(shape = NA, alpha = 0.6,
                                             colour = "#2a2a2a")),
    shape = guide_legend(order = 1,
                         override.aes = list(colour = "grey40", size = 5))
  ) +

  theme_mem() +
  theme(
    legend.position    = "bottom",
    legend.title       = element_text(face = "bold", size = 10, colour = INK),
    legend.text        = element_text(size = 10),
    legend.key.size    = unit(1.1, "lines"),
    legend.spacing.x   = unit(0.5, "cm"),
    axis.text.x        = element_text(size = 10, colour = MID),
    panel.grid.major.x = element_blank(),
    plot.margin = margin(t = 10, r = 15, b = 30, l = 10)
  )
```


### Old Version 3
```{r fig.width=7.5, fig.height=5.5}
subj_acc <- conf_df %>%
  group_by(subjId, enCon_label, reCon_label) %>%
  summarise(accuracy = mean(trial_accuracy), .groups = "drop") %>%
  rename(enc = enCon_label, rec = reCon_label) %>%
  mutate(
    enc     = factor(enc, levels = c("Single", "Repeats", "Triplets")),
    rec     = factor(rec, levels = c("Within Session", "Across Sessions")),
    x_group = factor(
      interaction(rec, enc, sep = "__"),
      levels = levels(emm$x_group)   # reuse levels from emm — single source of truth
    )
  )

ggplot() +

  # Vertical divider between recall groups
  annotate("segment",
         x = 3.5, xend = 3.5, y = 0.48, yend = 1.02,
         colour = "#DEDEDE", linewidth = 1.2) +

  # Group header labels
  annotate("text", x = 2, y = 0.485, label = "Within Session",
           hjust = 0.5, vjust = 1, size = 4, fontface = "bold", colour = INK) +
  annotate("text", x = 5, y = 0.485, label = "Across Sessions",
           hjust = 0.5, vjust = 1, size = 4, fontface = "bold", colour = INK) +

  # Layer 1: 95% CI error bars with caps on both ends.
  # Upper CI capped at 1.0 so the top cap is always visible —
  # without this, near-ceiling Within Session conditions produce
  # model CIs above 100% that get clipped by the axis, making
  # it look like only the bottom cap is shown.
  geom_errorbar(
    data  = emm %>% mutate(upper = pmin(upper, 1.0)),
    aes(x = x_group, ymin = lower, ymax = upper, colour = enc),
    width = 0.25, linewidth = 1.1
  ) +

  # Layer 2: Individual participant points — fixed per-participant offsets.
  # All three participants get a distinct x offset so nobody sits on the
  # CI line or stacks on another point. Offsets are deterministic (not random)
  # so the plot is fully reproducible without a seed.
  #   Participant 1 (subjId 3): -0.22 (left)
  #   Participant 2 (subjId 4): +0.10 (right of centre — off the CI line)
  #   Participant 3 (subjId 5): +0.22 (right)
  geom_point(
    data     = subj_acc %>% filter(subjId == "3"),
    aes(x = x_group, y = accuracy, colour = enc, shape = subjId),
    position = position_nudge(x = -0.22),
    size = 4, alpha = 0.75, stroke = 0.8
  ) +
  geom_point(
    data     = subj_acc %>% filter(subjId == "4"),
    aes(x = x_group, y = accuracy, colour = enc, shape = subjId),
    position = position_nudge(x = 0.10),
    size = 4, alpha = 0.75, stroke = 0.8
  ) +
  geom_point(
    data     = subj_acc %>% filter(subjId == "5"),
    aes(x = x_group, y = accuracy, colour = enc, shape = subjId),
    position = position_nudge(x = 0.22),
    size = 4, alpha = 0.75, stroke = 0.8
  ) +

  # Layer 3: Model-estimated mean (drawn last — always on top)
  geom_point(
    data   = emm,
    aes(x = x_group, y = estimate, fill = enc),
    shape  = 21, size = 8, stroke = 2.8,
    colour = "white"
  ) +

  scale_colour_manual(values = enc_pal, name = "Encoding Condition") +
  scale_fill_manual(values   = enc_pal, guide = "none") +
  scale_shape_manual(
    values = subj_shapes,
    name   = "Participant",
    labels = c("3" = "1", "4" = "2", "5" = "3")
  ) +
  scale_x_discrete(labels = x_labels) +
  scale_y_continuous(
    limits = c(0.47, 1.02),
    breaks = c(0.5, 0.6, 0.7, 0.8, 0.9, 1.0),
    labels = percent_format()
  ) +

  labs(
    title    = "Memory Accuracy Across Conditions",
    x        = "Recall Condition",
    y        = "Accuracy",
    caption  = NULL
  ) +

  guides(
    colour = guide_legend(order = 2,
                          override.aes = list(shape = 16, size = 4, alpha = 1)),
    shape  = guide_legend(order = 1,
                          override.aes = list(colour = "grey40", size = 4, alpha = 1))
  ) +

  theme_mem() +
  theme(
    legend.position  = "bottom",
    legend.title     = element_text(face = "bold", size = 10, colour = INK),
    legend.text      = element_text(size = 10),
    legend.spacing.x = unit(0.5, "cm")
  )
```


# Accuracy vs. Sleep Quality

## Column {data-width="650"}

### Final Version


```{r}
raw_df <- read.csv("combined_data.csv")

raw_df$subjId <- as.factor(raw_df$subjId)
raw_df$session <- as.factor(raw_df$session)

survey <- read_excel("Survey.xlsx")

survey$subjId <- as.factor(survey$subjId)
survey$session <- as.factor(survey$session)

accuracy <- raw_df %>%
  group_by(subjId, session) %>%
  summarise(
    accuracy = mean(trial_accuracy, na.rm = TRUE),
    .groups = "drop"
  )

survey_accuracy <- left_join(accuracy, survey, by = c("subjId", "session"))
```

```{r fig.width=10, fig.height=6}
subj_colors <- c("3" = "#009E73", "4" = "#0072B2", "5" = "#CC79A7")

ggplot(survey_accuracy, aes(x = sleep, y = accuracy, color = factor(subjId))) +
  geom_point(size = 2.5, alpha = 0.2) +
  
  # group average line
  geom_smooth(inherit.aes = FALSE,
              aes(x = sleep, y = accuracy),
              method = "lm", se = TRUE,
              color = "gray20", fill = "gray80",
              linewidth = 1.2, linetype = "longdash", alpha = 0.5) +
  
  geom_smooth(method = "lm", se = FALSE, linewidth = 1.2) +
  scale_color_manual(
  values = c("3" = scales::alpha("#009E73", 0.7), 
             "4" = scales::alpha("#0072B2", 0.7), 
             "5" = scales::alpha("#CC79A7", 0.7)),
  labels = c("Participant 1", "Participant 2", "Participant 3")
) +
  scale_x_continuous(breaks = 1:5, limits = c(1, 5)) +
  scale_y_continuous(
    limits = c(0.5, 1),
    labels = scales::percent_format(accuracy = 1)
  ) +
  labs(
    title = "Improved Sleep Quality Minimally Aids Memory Accuracy ",
    x = "Subjective Sleep Quality",
    y = "Accuracy",
    color = NULL
  ) +
  theme_minimal() +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_line(color = "gray85", linewidth = 0.5),
    axis.line = element_blank(),
    axis.ticks = element_blank(),
    plot.title = element_text(hjust = 0, size = 22, face = 'bold', margin = margin(b = 10)),
    plot.subtitle = element_text(hjust = 0, size = 12, color = 'gray50', margin = margin(b = 15)),
    legend.position = "bottom",
    #legend.text = element_text(size = 10),
    legend.title= element_text(face = 'bold', size = 13, colour = 'gray30'),
    legend.text = element_text(size = 12),
    axis.title.x= element_text(size = 16, colour = 'gray30'),
    axis.title.y = element_text(size = 17, colour = 'gray30'),
    axis.text = element_text(size = 13, colour = 'gray30'),
    plot.margin = margin(t = 10, r = 15, b = 30, l = 10)
  )
```

## Column {.tabset data-width="350"}

### About

**Research Question:** Does memory performance differ based on how sleepy participants are?

&nbsp;

**Hypothesis:** Memory performance will decrease when subjects are sleepy.

&nbsp;

**Conclusion:** The overall correlation is not statistically significant (*r* = 0.16, *p* = 0.29), so we cannot conclude there's a reliable relationship. The data does not support our hypothesis that better sleep quality predicts higher accuracy, at least not in this small sample. Future data collection can help elucidate these relationships.

&nbsp;

```{r}
# Descriptive statistics: Sleep Quality vs Memory Accuracy
sleep_desc <- survey_accuracy %>%
  group_by(sleep) %>%
  summarise(
    N    = n(),
    Mean = mean(accuracy, na.rm = TRUE),
    SD   = sd(accuracy, na.rm = TRUE),
    Min  = min(accuracy, na.rm = TRUE),
    Max  = max(accuracy, na.rm = TRUE),
    .groups = "drop"
  )

# Pearson correlation
sleep_cor <- cor.test(survey_accuracy$sleep, survey_accuracy$accuracy)

# Print table
sleep_desc %>%
  gt() %>%
  tab_header(
    title    = "Memory Accuracy by Sleep Quality",
    subtitle = "Each row = one session (N = 45 sessions across 3 subjects)"
  ) %>%
  cols_label(
    sleep = "Sleep Quality",
    N     = "N (sessions)",
    Mean  = "Mean Accuracy",
    SD    = "SD",
    Min   = "Min",
    Max   = "Max"
  ) %>%
  fmt_percent(columns = c(Mean, SD, Min, Max), decimals = 1) %>%
  tab_footnote(
    footnote  = "Min/Max reflect subject-level session means (n = 3 subjects).",
    locations = cells_column_labels(columns = c(Min, Max))
  ) %>% 
  tab_style(
    style     = cell_text(weight = "bold"),
    locations = cells_column_labels()
  ) %>%
  opt_row_striping() %>%
  opt_table_font(font = google_font("IBM Plex Sans"))
```

### Old Version 1

```{r}
subj_colors <- c("3" = "#5B8FCC", "4" = "#E8855A", "5" = "#5BAF8F")  # blue, orange, green

ggplot(survey_accuracy, aes(x = sleep, y = accuracy, color = factor(subjId))) +
  geom_point(size = 2.5, alpha = 0.8) +
  geom_smooth(method = "lm", se = FALSE, linewidth = 1.2) +
  scale_color_manual(
    values = subj_colors,
    labels = c("Participant 1", "Participant 2", "Participant 3")
  ) +
  scale_x_continuous(breaks = 1:5, limits = c(1, 5)) +
  scale_y_continuous(
    limits = c(0.7, 1),
    labels = scales::percent_format(accuracy = 1)
  ) +
  labs(
    title = "Accuracy by Sleep Quality",
    x = "Sleep Quality",
    y = "Accuracy",
    color = NULL
  ) +
  theme_minimal() +
  theme(
    #plot.background = element_rect(fill = "#F5F0EB", color = NA),
    #panel.background = element_rect(fill = "#F5F0EB", color = NA),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_line(color = "gray85", linewidth = 0.5),
    axis.line = element_blank(),
    axis.ticks = element_blank(),
    plot.title = element_text(hjust = 0, size = 14, face = "bold", margin = margin(b = 10)),
    legend.position = "bottom",
    legend.text = element_text(size = 10),
    axis.title = element_text(size = 11, color = "gray30"),
    axis.text = element_text(size = 10, color = "gray30")
  )
```


### Old Version 2

```{r}
ggplot(survey_accuracy, aes(x = sleep, y = accuracy, color = factor(subjId))) +
  geom_point(size = 2.5, alpha = 0.2) +
  
  
  geom_smooth(method = "lm", se = FALSE, linewidth = 1.2) +
  scale_color_manual(
  values = c("3" = scales::alpha("#009E73", 0.7), 
             "4" = scales::alpha("#0072B2", 0.7), 
             "5" = scales::alpha("#CC79A7", 0.7)),
  labels = c("Participant 1", "Participant 2", "Participant 3")
) +
  scale_x_continuous(breaks = 1:5, limits = c(1, 5)) +
  scale_y_continuous(
    limits = c(0.7, 1),
    labels = scales::percent_format(accuracy = 1)
  ) +
  labs(
    title = "Improved Sleep Quality Aids Memory Accuracy ",
    x = "Sleep Quality",
    y = "Memory Accuracy",
    color = NULL
  ) +
  theme_minimal() +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_line(color = "gray85", linewidth = 0.5),
    axis.line = element_blank(),
    axis.ticks = element_blank(),
    plot.title = element_text(hjust = 0, size = 14, face = "bold", margin = margin(b = 10)),
    legend.position = "bottom",
    legend.text = element_text(size = 10),
    axis.title = element_text(size = 11, color = "gray30"),
    axis.text = element_text(size = 10, color = "gray30")
  )
```


# Accuracy vs. Voice
## Column {data-width="650"}

### Final Version
```{r voiceSetup}
# ZC setup --------------------------------------------------------------

# Constants 
VOICE_LEVELS <- c("nova", "echo", "onyx", "shimmer")
VOICE_LABELS <- c("Nova", "Echo", "Onyx", "Shimmer")
VOICE_PAL_old <- c(
  nova    = "#7B2D8B",  # amethyst purple
  echo    = "#C0392B",  # ruby red
  onyx    = "#1A6B8A",  # sapphire blue
  shimmer = "#D4A017"   # golden amber
)

# Prepare data
df_voice <- raw_df %>%
  filter(!is.na(recog), !is.na(correct_resp), !is.na(voice)) %>%
  mutate(
    correct = as.integer(as.character(correct_resp) == as.character(recog)),
    voice   = factor(voice, levels = VOICE_LEVELS)
  )
# ── Summaries ──────────────────────────────────────────────────────────────────
subj_acc <- df_voice %>%
  group_by(subjId, voice) %>%
  summarise(accuracy = mean(correct), .groups = "drop")

group_acc <- df_voice %>%
  group_by(voice) %>%
  summarise(
    mean_acc = mean(correct),
    se_acc   = sd(correct) / sqrt(n()),
    .groups  = "drop"
  )
```

```{r fig.width=10, fig.height=6}
VOICE_PAL <- c(
  nova    = "#0072B2",  # deep blue
  echo    = "#E69F00",  # orange
  onyx    = "#009E73",  # teal-green
  shimmer = "#CC79A7"   # pink-purple
)

# Define shapes
subj_shapes  <- c("3" = 15, "4" = 17, "5" = 16)  # square, triangle, circle

# Add x_offset AND shape column to subj_acc
subj_acc <- df_voice %>%
  group_by(subjId, voice) %>%
  summarise(accuracy = mean(correct), .groups = "drop") %>%
  group_by(voice) %>%
  mutate(x_offset = (row_number() - 2) * 0.12) %>%
  ungroup() %>%
  mutate(subjId = factor(subjId))

# ── Plot ───────────────────────────────────────────────────────────────────────
ggplot(group_acc, aes(x = voice, y = mean_acc, fill = voice)) +
  #geom_hline(yintercept = 0.5, linetype = "dotted", color = "gray60", linewidth = 0.7) +
  #annotate("text", x = 0.55, y = 0.515, label = "chance", size = 3.5, color = "gray50", hjust = 0) +
  geom_linerange(
    aes(x = voice, ymin = 0.5, ymax = mean_acc, colour = voice),
    linewidth = 30, alpha = 0.85
  ) +
  geom_point(
    data = subj_acc,
    aes(x = as.numeric(voice) + x_offset, y = accuracy,
        color = voice, shape = subjId),
    size = 5.5, alpha = 0.7, stroke = 0.8
  ) +
  geom_errorbar(
    aes(ymin = mean_acc - se_acc, ymax = mean_acc + se_acc),
    width = 0.15, linewidth = 0.8, color = "gray30"
  ) +
  scale_fill_manual(values = VOICE_PAL, guide = "none") +
  scale_color_manual(values = VOICE_PAL, guide = "none") +
  scale_shape_manual(
    values = subj_shapes,
    name   = "Participant",
    labels = c("3" = "1", "4" = "2", "5" = "3")
  ) +
  scale_x_discrete(labels = VOICE_LABELS) +
  scale_y_continuous(
  limits = c(0.5, 1.05), breaks = seq(0.5, 1, 0.1),
  labels = function(x) paste0(round(x * 100), "%"),
  expand = c(0, 0)
  ) +
  labs(
    title    = "Voice Type Does Not Affect Memory Accuracy",
    # subtitle = "Mean accuracy ± SE (shapes = individual subjects)",
    x = "Voice", y = "Accuracy"
  ) +
  guides(
    shape = guide_legend(
      order = 1,
      override.aes = list(colour = "grey40", size = 4, alpha = 1)
    )
  ) +
  theme_minimal(base_size = 14, base_family = "ibm") +
  theme(
    plot.background    = element_rect(fill = "white", colour = NA),
    panel.background   = element_rect(fill = "white", colour = NA),
    panel.grid.major.x = element_blank(),
    panel.grid.minor   = element_blank(),
    panel.grid.major.y = element_line(color = "gray85", linewidth = 0.5),
    axis.ticks         = element_blank(),
    plot.title         = element_text(hjust = 0, size = 22, face = "bold", margin = margin(b = 10)),
    plot.subtitle      = element_text(hjust = 0, size = 12, color = "gray50", margin = margin(b = 15)),
    legend.position    = "bottom",
    legend.title       = element_text(face = "bold", size = 13, colour = "gray30"),
    legend.text        = element_text(size = 12),
    axis.title.x       = element_text(size = 16, colour = "gray30"),
    axis.title.y       = element_text(size = 17, colour = "gray30"),
    axis.text          = element_text(size = 13, colour = "gray30"),
    plot.margin        = margin(t = 10, r = 15, b = 30, l = 10)
  )
```


## Column {.tabset data-width="350"}

### About

**Research Question:** Does pitch or gender of voice affect how we remember pairings?

&nbsp;

**Hypothesis:** Voice type will not affect memory performance, and this will remain consistent across sessions.

&nbsp;

**Conclusion:** Voice type does not meaningfully affect memory accuracy. All four voices (Nova, Echo, Onyx, Shimmer) cluster tightly between 86–91%, with overlapping error bars suggesting no reliable differences. Participant 2 (triangles) shows consistently lower accuracy across all voices, indicating individual differences outweigh any voice type effect.

&nbsp;


```{r voiceDesc}
# Trial counts at trial level
trial_counts <- df_voice %>%
  group_by(voice) %>%
  summarise(Trials = n(), .groups = "drop")

# Subject-level means
subj_voice_acc <- df_voice %>%
  group_by(subjId, voice) %>%
  summarise(subj_acc = mean(correct), .groups = "drop")

# Summarise across subjects, then join trial counts
desc_voice <- subj_voice_acc %>%
  group_by(voice) %>%
  summarise(
    Mean = mean(subj_acc),
    SD   = sd(subj_acc),
    Min  = min(subj_acc),
    Max  = max(subj_acc),
    .groups = "drop"
  ) %>%
  left_join(trial_counts, by = "voice") %>%
  select(voice, Trials, Mean, SD, Min, Max) %>%
  mutate(voice = factor(voice, levels = VOICE_LEVELS, labels = VOICE_LABELS))

desc_voice %>%
  gt() %>%
  tab_header(
    title    = "Memory Accuracy by Voice Type",
    subtitle = "Descriptive statistics across all trials and subjects"
  ) %>%
  cols_label(
    voice  = "Voice",
    Trials = "N (trials)",
    Mean   = "Mean Accuracy",
    SD     = "SD",
    Min    = "Min",
    Max    = "Max"
  ) %>%
  fmt_percent(columns = c(Mean, SD, Min, Max), decimals = 1) %>%
  tab_footnote(
    footnote = "Min/Max reflect subject-level means (n = 3 subjects per voice).",
    locations = cells_column_labels(columns = c(Min, Max))
  ) %>%
  tab_style(
    style     = cell_text(weight = "bold"),
    locations = cells_column_labels()
  ) %>%
  opt_row_striping() %>%
  opt_table_font(font = google_font("IBM Plex Sans"))
```

### Old Version 1 
```{r v1}
ggplot(group_acc, aes(x = voice, y = mean_acc, fill = voice)) +
  geom_hline(yintercept = 0.5, linetype = "dotted", color = "gray60", linewidth = 0.7) +
  annotate("text", x = 0.55, y = 0.515, label = "chance", size = 3.5, color = "gray50", hjust = 0) +
  geom_col(width = 0.55, alpha = 0.85) +
  geom_point(
    data = subj_acc,
    aes(x = voice, y = accuracy, color = voice),
    position = position_jitter(width = 0.1, seed = 7),
    size = 3.5, alpha = 0.7, shape = 16
  ) +
  geom_errorbar(
    aes(ymin = mean_acc - se_acc, ymax = mean_acc + se_acc),
    width = 0.15, linewidth = 0.8, color = "gray30"
  ) +
  scale_fill_manual(values = VOICE_PAL_old, guide = "none") +
  scale_color_manual(values = VOICE_PAL_old, guide = "none") +
  scale_x_discrete(labels = VOICE_LABELS) +
  scale_y_continuous(
    limits = c(0, 1.05), breaks = seq(0, 1, 0.25),
    labels = function(x) paste0(round(x * 100), "%"),
    expand = c(0, 0)
  ) +
  labs(
    title = "Voice Type Does Not\nAffect Memory",
    subtitle = "Mean accuracy ± SE · dots = individual subjects",
    x = "Voice", y = "Accuracy"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.background    = element_rect(fill = "white", colour = NA),
    panel.background   = element_rect(fill = "white", colour = NA),
    panel.grid.major.x = element_blank(),
    panel.grid.minor   = element_blank(),
    panel.grid.major.y = element_line(color = "gray85", linewidth = 0.5),
    axis.line          = element_blank(),
    axis.ticks         = element_blank(),
    plot.title         = element_text(hjust = 0, size = 22, face = "bold", margin = margin(b = 10)),
    plot.subtitle      = element_text(hjust = 0, size = 12, color = "gray50", margin = margin(b = 15)),
    axis.title.x       = element_text(size = 16, colour = "gray30"),
    axis.title.y       = element_text(size = 17, colour = "gray30"),
    axis.text          = element_text(size = 13, colour = "gray30"),
    plot.margin        = margin(t = 10, r = 15, b = 30, l = 10)
  )
```


### Old Version 2
```{r v2}
# make them all offsets the same
subj_acc <- subj_acc %>%
  group_by(voice) %>%
  mutate(x_offset = (row_number() - 2) * 0.12) %>%  # always: -0.12, 0, +0.12
  ungroup()

# plot
ggplot(group_acc, aes(x = voice, y = mean_acc, fill = voice)) +
  geom_hline(yintercept = 0.5, linetype = "dotted", color = "gray60", linewidth = 0.7) +
  annotate("text", x = 0.55, y = 0.515, label = "chance", size = 3.5, color = "gray50", hjust = 0) +
  geom_col(width = 0.55, alpha = 0.85) +
  geom_point(
  data = subj_acc,
  aes(x = as.numeric(voice) + x_offset, y = accuracy, color = voice),
  size = 5.5, alpha = 0.7, shape = 16
  ) +
  geom_errorbar(
    aes(ymin = mean_acc - se_acc, ymax = mean_acc + se_acc),
    width = 0.15, linewidth = 0.8, color = "gray30"
  ) +
  scale_fill_manual(values = VOICE_PAL_old, guide = "none") +
  scale_color_manual(values = VOICE_PAL_old, guide = "none") +
  scale_x_discrete(labels = VOICE_LABELS) +
  scale_y_continuous(
    limits = c(0, 1.05), breaks = seq(0, 1, 0.25),
    labels = function(x) paste0(round(x * 100), "%"),
    expand = c(0, 0)
  ) +
  labs(
    title = "Voice Type Does Not\nAffect Memory",
    subtitle = "Mean accuracy ± SE · dots = individual subjects",
    x = "Voice", y = "Accuracy"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.background    = element_rect(fill = "white", colour = NA),
    panel.background   = element_rect(fill = "white", colour = NA),
    panel.grid.major.x = element_blank(),
    panel.grid.minor   = element_blank(),
    panel.grid.major.y = element_line(color = "gray85", linewidth = 0.5),
    axis.line          = element_blank(),
    axis.ticks         = element_blank(),
    plot.title         = element_text(hjust = 0, size = 22, face = "bold", margin = margin(b = 10)),
    plot.subtitle      = element_text(hjust = 0, size = 12, color = "gray50", margin = margin(b = 15)),
    axis.title.x       = element_text(size = 16, colour = "gray30"),
    axis.title.y       = element_text(size = 17, colour = "gray30"),
    axis.text          = element_text(size = 13, colour = "gray30"),
    plot.margin        = margin(t = 10, r = 15, b = 30, l = 10)
  )
```


### Old Version 3
```{r v3}
# Define shapes
subj_shapes  <- c("3" = 15, "4" = 17, "5" = 16)  # square, triangle, circle

# Add x_offset AND shape column to subj_acc
subj_acc <- df_voice %>%
  group_by(subjId, voice) %>%
  summarise(accuracy = mean(correct), .groups = "drop") %>%
  group_by(voice) %>%
  mutate(x_offset = (row_number() - 2) * 0.12) %>%
  ungroup() %>%
  mutate(subjId = factor(subjId))

# ── Plot ───────────────────────────────────────────────────────────────────────
ggplot(group_acc, aes(x = voice, y = mean_acc, fill = voice)) +
  geom_hline(yintercept = 0.5, linetype = "dotted", color = "gray60", linewidth = 0.7) +
  annotate("text", x = 0.55, y = 0.515, label = "chance", size = 3.5, color = "gray50", hjust = 0) +
  geom_col(width = 0.55, alpha = 0.85) +
  geom_point(
    data = subj_acc,
    aes(x = as.numeric(voice) + x_offset, y = accuracy,
        color = voice, shape = subjId),
    size = 5.5, alpha = 0.7, stroke = 0.8
  ) +
  geom_errorbar(
    aes(ymin = mean_acc - se_acc, ymax = mean_acc + se_acc),
    width = 0.15, linewidth = 0.8, color = "gray30"
  ) +
  scale_fill_manual(values = VOICE_PAL_old, guide = "none") +
  scale_color_manual(values = VOICE_PAL_old, guide = "none") +
  scale_shape_manual(
    values = subj_shapes,
    name   = "Participant",
    labels = c("3" = "1", "4" = "2", "5" = "3")
  ) +
  scale_x_discrete(labels = VOICE_LABELS) +
  scale_y_continuous(
    limits = c(0, 1.05), breaks = seq(0, 1, 0.25),
    labels = function(x) paste0(round(x * 100), "%"),
    expand = c(0, 0)
  ) +
  labs(
    title = "Voice Type Does Not\nAffect Memory",
    subtitle = "Mean accuracy ± SE (shapes = individual subjects)",
    x = "Voice", y = "Accuracy"
  ) +
  guides(
    shape = guide_legend(
      order = 1,
      override.aes = list(colour = "grey40", size = 4, alpha = 1)
    )
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.background    = element_rect(fill = "white", colour = NA),
    panel.background   = element_rect(fill = "white", colour = NA),
    panel.grid.major.x = element_blank(),
    panel.grid.minor   = element_blank(),
    panel.grid.major.y = element_line(color = "gray85", linewidth = 0.5),
    axis.ticks         = element_blank(),
    plot.title         = element_text(hjust = 0, size = 22, face = "bold", margin = margin(b = 10)),
    plot.subtitle      = element_text(hjust = 0, size = 12, color = "gray50", margin = margin(b = 15)),
    legend.position    = "bottom",
    legend.title       = element_text(face = "bold", size = 13, colour = "gray30"),
    legend.text        = element_text(size = 12),
    axis.title.x       = element_text(size = 16, colour = "gray30"),
    axis.title.y       = element_text(size = 17, colour = "gray30"),
    axis.text          = element_text(size = 13, colour = "gray30"),
    plot.margin        = margin(t = 10, r = 15, b = 30, l = 10)
  )
```



